%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Robotics Engineer \& Product Owner – Localization} % Job title
    {Navya Mobility} % Organization
    {Paris, France} % Location
    {Jun. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Refactored and modularized legacy stack; reduced debugging time by 40\%
        \item Designed localization KPIs and developed framework to track their evolution across releases.
        \item Built MCAP + Foxglove-based log visualizer with monitoring dashboards
        \item Improving LiDAR ICP pipeline for better edge‑case resilience and multi‑sensor fusion.
        \item Currently designing a new SLAM framework to benefit both localization and mapping teams.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Robotics Engineer} % Job title
    {FORSSEA Robotics} % Organization
    {Paris/Frontignan, France} % Location
    {2019 - 2024} % Date(s)
    {
      \begin{cvitems}
        \item Led the migration from ROS1 to ROS2 and re-architected the robotic software stack for a commercial underwater ROV.
        \item Adapted Nav2 and MoveIt2 for full 3D navigation and autonomous docking, enabling rapid algorithm experimentation.
        \item Migrated codebase to modern C++, introduced unit tests, and set up CI/CD with GitHub Actions, JFrog, and Docker.
        \item Maintained Gazebo simulation, authored custom plugins, and contributed fixes upstream.
        \item Participated in sea trials and real-world deployments in Brazil and Norway.
        \item Guided hiring and mentorship of new engineers; advised CTO on roadmap priorities using JIRA epics.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Robotics Engineer} % Job title
    {FORSSEA Robotics} % Organization
    {Paris/Frontignan, France} % Location
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Owned software architecture in ROS1 for autonomous ROV: path following, visual docking, and localization.
        \item Developed a flexible EKF implementation used to test various sensor set configurations.
        \item Implemented visual SLAM with fiducial markers (Aruco).
        \item Wrote and improved low-level drivers for work-class ROV hardware.
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
  %  {Robotics Intern} % Job title
  %  {FORSSEA Robotics} % Organization
  %  {Paris/Frontignan, France} % Location
  %  {Mar. - Sept. 2017} % Date(s)
  %  {
  %    \begin{cvitems} % Description(s) of tasks/responsibilities
  %      \item Developed multi‑sensor EKF pose estimator fusing underwater sensor sets (LBL, USBL, DVL, Camera) and thrust allocation for underwater ROV in MORSE/ROS.
  %      \item Contributed to motion control modules and simulator enhancements.
  %    \end{cvitems}
  %  }


%---------------------------------------------------------
  \cventry
    {Freelance Robotics Consultant} % Job title
    {Fiverr / Upwork} % Organization
    {Remote} % Location
    {2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Supported integration of ROS2 Fleet Management (RMF) for a client’s logistics robot prototype.
        \item Built simulation environments for robotic arms and integrated them with MoveIt2.
        \item Supported agricultural robotics development, including sensor integration and localization
        \item Developed and debugged custom hardware drivers.
        \item Providing ROS2\_control training to engineers and teams.
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
